A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-19 papers/execution-model/model.tex
Add files via upload
revised Sec-3 and Sec-6

\section{Execution Model}
\label{sec:execution-model}
The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
blockchains. Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should  upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.

In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful. An implicit account is a non-programmable account and is associated with a pair of private/public keys. A smart contract is a programmable account created by an origination operation and has no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. All existing accounts are stored in a context component on the blockchain. An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. Tezos provides the Michelson language for writing a smart contract. Michelson is a stack-based language with strict static type checking. A contract is a function that maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. The script of a smart contract must be type-checked before it is introduced into the system.

An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a new smart contract.E ach transaction includes the address of the sender contract, the address of the destination contract, the amount of tokens transferred, and a fee to be paid either by payment to a baker or by destruction (burning). In addition, a smart contract invocation must provide input data and and an origination transaction specifies the script of the contract and the initial content of the contract storage.  A transaction can only be sent if it has been signed with the sender contract's private key. It is then injected into the blockchain network via a node that runs the gossip network and updates the context. The node first validates the transaction before submitting it to the network. In general, a transaction can fail for a number of reasons, including incorrect destination address, insufficient balances, incorrect counters, and incorrect type of input parameters (or scripts). A transaction is valid only if the counter of the sender contract is the same as the counter  used in the transaction. The invocation of a smart contract may fail for reasons determined by the contract's script. An invalid transaction is rejected by the node.

Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. On the other hand, a pending transaction may get lost in the mempool. That is, it may be dropped. There are several
causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation. A transaction is timed out when 60 blocks have passed and it can no longer be included in a block. When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed. Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.

@@

>>>>

\section{Execution Model}
\label{sec:execution-model}
The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established blockchains. Tezos proposes an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and nodes should upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.

In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are a programmable account created by an origination operation and have no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. An implicit account is maintained on the blockchain with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. A contract script maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. An implicit account performs three kinds of transactions: (1) transfer tokens to another implicit account, (2) invoke a smart contract, or (3) originate a new smart contract. A contract origination specifies the script of the contract and the initial contents of the contract storage, while a contract invocation must provide input data. Each transaction contains a fee to be paid either by payment to a baker or by destruction (burning). A transaction is injected into the blockchain network via a node, which then validates the transaction before submitting it to the network. Generally, a transaction can be rejected by the node for a number of reasons. Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. On the other hand, a pending transaction can be lost in the mempool. A transaction is timed out when 60 blocks have passed and it can no longer be included in a block. When a transaction is included in a blockchain, the related accounts are updated according to the transaction result.

@@

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of smart contracts. Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network. A blockchain oracle is used to provide external data to smart contracts. Several researches have been done to provide oracle solutions for blockchain. The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles. This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications. Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain. For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum. The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$. 
For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.

The main issues in using a blockchain oracle are trust and security \cite{trustworthy}. The researchers in \cite{reliable-oracle} have proposed a decentralized oracle to verify the interactions and solve the disputes between blockchain smart contracts and oracles. Similarly, researchers in \cite{reliablity-oracles} focus on the notion of trust and provide a framework to perform reliability analysis of various blockchain oracle platforms. Closely following our work, in \cite{interact-coq} the authors present a model-executable specification of smart-contract execution in Coq. Their formalizations target Ethereum and Tezos.
